Multi-EWAS enrichment example

### 2024-01-16 figs/multi_ewas_example.Rmd
fix bug with missing conds
resize text

top <- mtable2[which(mtable2$set %in% gsets),]
top <- top[,c(1,4:17)]
rownames(top) <- top$set
top$set=NULL
head(top,2)

@@

pdf("fig8d.pdf",height=9,width=7)
heatmap.2(as.matrix(top),scale="none",trace="none",margins=c(6,20),
  col=colfunc(25),cexRow=0.5,cexCol=0.8)
dev.off()

>>>>

top <- mtable2[which(mtable2$set %in% gsets),]
top <- top[,c(1,4:22)]
rownames(top) <- top$set
top$set=NULL
head(top,2)

@@

pdf("fig8d.pdf",height=9,width=7)
heatmap.2(as.matrix(top),scale="none",trace="none",margins=c(6,20),
  col=colfunc(25),cexRow=0.5,cexCol=0.7)
dev.off()
